On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-10-22 paper.tex
Rewording

Consider $a=b=1$ first. This is illustrated in Figure~\ref{fig: ijLS_1}. Note that in this and in the next figures the axes represent $ia$ and $jb$ (not $i$ and $j$). It is convenient, however, to refer to the point $(ia,jb)$ by its normalized coordinates $(i,j)$. In this graph, each dashed diagonal line contains pairs $(i,j)$ with the same $i+j-1$; and the lower bound \eqref{eq: len > sqrt} corresponds to an arc centered at normalized coordinates $(2,2)$.

>>>>

Consider $a=b=1$ first. This is illustrated in Figure~\ref{fig: ijLS_1}. Note that in this and in the next figures the axes represent $ia$ and $jb$, rather than normalized coordinates $i$ and $j$. In this graph, each dashed diagonal line contains pairs $(i,j)$ with the same $i+j-1$; and the lower bound \eqref{eq: len > sqrt} corresponds to an arc centered at normalized coordinates $(2,2)$.
